The SMT Competition 2015--2018

### 2019-04-09 2018/report/SMT-COMP.tex
Report: Split participants table, description.

\usepackage{jsat}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{booktabs}
\usepackage{longtable}
%\usepackage[pdf]{pstricks}
%\usepackage{pst-tree}

@@

Table~\ref{table:participants} lists the solvers that participated
between~2015 and~2018, together with their submitter(s) and
institutional affiliations (which may have changed over time).  Note
that most solvers were developed by a group of people; the table does
not list all contributors but only submitters.
%
Participants are also encouraged to submit a short system description
of their solver, including a list of its authors and an explanation of
the SMT solving approach used.  System descriptions are published on
the competition website.  They were submitted for about 60\,\% of all
solver versions since 2015.

>>>>

\usepackage{jsat}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{booktabs}
%\usepackage[pdf]{pstricks}
%\usepackage{pst-tree}

@@

Tables~\ref{table:participants1}-\ref{table:participants3} list the solvers
that participated between~2015 and~2018, together with contributing team
members (in alphabetical order) and their institutional affiliations (which may
have changed over time).
%
Participants are also encouraged to submit a short system description
of their solver, including a list of its authors and an explanation of
the SMT solving approach used.  System descriptions are published on
the competition website.  They were submitted for about 60\,\% of all
solver versions since 2015.
